### 2018-12-12 main-plos.tex
tailing whitespace
break lines, etc
removed comments
abstract; macros etc
removed Author summary

% Use Unicode characters when possible
\usepackage[utf8x]{inputenc}

@@

% Use nameref to cite supporting information files (see Supporting Information section for more info)
\usepackage{nameref,hyperref}

@@

@@

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
% Please use "sentence case" for title and headings (capitalize only the first
% word in a title (or heading), the first word in a subtitle (or subheading),
% and any proper nouns).
% % \title{Machine learning of prostate MRI: towards improved non-invasive
% % prostate cancer characterization}
\textbf\newline{Machine learning of prostate MRI:\ towards improved non-invasive
prostate cancer characterization}
}
\newline
% Insert author names, affiliations and corresponding author email (do not
% include titles, positions, or degrees).
% % \author[dia,inf]{Jussi~Toivonen\corref{cor1}}
% % \author[dia,inf]{Ileana~Montoya~Perez}
% % \author[dia,inf]{Parisa~Movahedi}
% % \author[dia,inf,pet]{Harri~Merisaari}
% % \author[dia]{Marko~Pesola}
% % \author[pat]{Pekka~Taimen}
% % \author[uro]{Peter~J.~Boström}
% % \author[inf]{Jonne~Pohjankukka}
% % \author[dia,med]{Aida~Kiviniemi}
% % \author[inf]{Tapio~Pahikkala}
% % \author[dia,med]{Hannu~J.~Aronen}
% % \author[dia,rad]{Ivan~Jambor}
\\
%Jussi Toivonen\textsuperscript{1,2*\textcurrency},
Jussi~Toivonen\textsuperscript{1,2*},
Ileana~Montoya~Perez\textsuperscript{1,2},
Parisa~Movahedi\textsuperscript{1,2},
Harri~Merisaari\textsuperscript{1,2,3},
Marko~Pesola\textsuperscript{1},
Pekka~Taimen\textsuperscript{4},
Peter~J.~Boström\textsuperscript{5},
Jonne~Pohjankukka\textsuperscript{2},
Aida~Kiviniemi\textsuperscript{1,6},
Tapio~Pahikkala\textsuperscript{2},
Hannu~J.~Aronen\textsuperscript{1,6},
Ivan~Jambor\textsuperscript{1,7}
\\
\bigskip
% % \address[dia]{Department of Diagnostic Radiology, \utu}
% % \address[inf]{Department of Information Technology, \utu}
% % \address[pet]{Turku PET Centre, \utu}
% % \address[pat]{Department of Pathology, University of Turku and \tyks}
% % \address[uro]{Department of Urology, \tyks}
% % \address[med]{Medical Imaging Centre of Southwest Finland, \tyks}
% % \address[rad]{Department of Radiology, University of Massachusetts---Baystate, Springfield, MA, USA}
%\textbf{1} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\textbf{1} \deptdr, \utu, \turku\\
\textbf{2} \deptft, \utu, \turku\\
\textbf{3} Turku PET Centre, \utu, \turku\\
\textbf{4} Dept.\ of Pathology, \utu{} and \tyks, \turku\\
\textbf{5} Dept.\ of Urology, \tyks, \turku\\
\textbf{6} Medical Imaging Centre of Southwest Finland, \tyks, \turku\\
\textbf{7} Dept.\ of Radiology, University of Massachusetts---Baystate,
Springfield, MA, USA\\
\bigskip

@@

\end{flushleft}
% Please keep the abstract below 300 words
\section*{Abstract}
Lorem ipsum dolor sit amet, consectetur adipiscing elit. Curabitur eget porta erat. Morbi consectetur est vel gravida pretium. Suspendisse ut dui eu ante cursus gravida non sed sem. Nullam sapien tellus, commodo id velit id, eleifend volutpat quam. Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus. Nunc pellentesque pretium diam, quis maximus dolor faucibus id. Nunc convallis sodales ante, ut ullamcorper est egestas vitae. Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.

% Please keep the Author Summary between 150 and 200 words
% Use first person. PLOS ONE authors please skip this step. 
% Author Summary not valid for PLOS ONE submissions.   
\section*{Author summary}
Lorem ipsum dolor sit amet, consectetur adipiscing elit. Curabitur eget porta erat. Morbi consectetur est vel gravida pretium. Suspendisse ut dui eu ante cursus gravida non sed sem. Nullam sapien tellus, commodo id velit id, eleifend volutpat quam. Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus. Nunc pellentesque pretium diam, quis maximus dolor faucibus id. Nunc convallis sodales ante, ut ullamcorper est egestas vitae. Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.

@@

@@

% Place tables after the first paragraph in which they are cited.
\begin{table}[!ht]
\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\caption{
{\bf Table caption Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam.}}
\begin{tabular}{|l+l|l|l|l|l|l|l|}
\hline
\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \thickhline
$cell1 row1$ & cell2 row 1 & cell3 row 1 & cell4 row 1 & cell5 row 1 & cell6 row 1 & cell7 row 1 & cell8 row 1\\ \hline
$cell1 row2$ & cell2 row 2 & cell3 row 2 & cell4 row 2 & cell5 row 2 & cell6 row 2 & cell7 row 2 & cell8 row 2\\ \hline
$cell1 row3$ & cell2 row 3 & cell3 row 3 & cell4 row 3 & cell5 row 3 & cell6 row 3 & cell7 row 3 & cell8 row 3\\ \hline
\end{tabular}
\begin{flushleft} Table notes Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl. Ut ornare mauris tellus, vel dapibus arcu suscipit sed.
\end{flushleft}
\label{table1}
\end{adjustwidth}
\end{table}

%PLOS does not support heading levels beyond the 3rd (no 4th level headings).
\subsection*{\lorem\ and \ipsum\ nunc blandit a tortor}
\subsubsection*{3rd level heading} 
Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque. Quisque augue sem, tincidunt sit amet feugiat eget, ullamcorper sed velit. Sed non aliquet felis. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Mauris commodo justo ac dui pretium imperdiet. Sed suscipit iaculis mi at feugiat.

@@

% Include only the SI item label in the paragraph heading. Use the \nameref{label} command to cite SI items in the text.
\paragraph*{S1 Fig.}
\label{S1_Fig}
{\bf Bold the title sentence.} Add descriptive text after the title of the item (optional).

@@

% \usepackage[utf8]{inputenc}
% \usepackage[T1]{fontenc}
% %\usepackage{latexsym}
% \usepackage[abbreviations = true]{siunitx}
% \usepackage{algorithmic, algorithm}
% %\hypersetup{colorlinks,%
% %    citecolor=blue,%
% %    filecolor=blue,%
% %    linkcolor=blue,%
% %    urlcolor=blue,%
% %    unicode
% %    }
% 
% \sisetup{detect-all = true,
%   text-rm = \sffamily,
%   per-mode = symbol,
%   literal-superscript-as-power = true
%   }
% %\DeclareSIUnit \umm{\square\um}
% \modulolinenumbers[5]
% 
% \floatname{algorithm}{Pseudo code}
% \renewcommand{\algorithmicrequire}{\textbf{Input:}}
% \renewcommand{\algorithmicensure}{\textbf{Output:}}
% \renewcommand{\algorithmiccomment}[1]{\hspace{1em}\emph{\{#1\}}}
% 
% %\newcommand{\tss}[1]{\textsubscript{#1}}
% %\newcommand{\tSs}[1]{\textsuperscript{#1}}
% 
% %%\newcommand{\texttwosuperior}{\(^2\)}  % Unicode character ²
% %\newcommand{\texttwosuperior}{\textsuperscript{2}}  % Unicode character ²
% %\newcommand{\texttimes}{\(\times\)}  % Unicode character ×
% %\newcommand{\textmu}{\(\mu\)}  % Unicode character ×
% 
% \renewcommand{\vec}[1]{\mathbf{#1}}  % Vectors and matrices.
% 
% %\DeclareUnicodeCharacter{03C3}{\(\sigma\)}
% \DeclareUnicodeCharacter{2096}{\text{\textsubscript{k}}}
% \DeclareUnicodeCharacter{2098}{\text{\textsubscript{m}}}
% \DeclareUnicodeCharacter{2081}{\text{\textsubscript{1}}}
% \DeclareUnicodeCharacter{2082}{\text{\textsubscript{2}}}
% \DeclareUnicodeCharacter{1D68}{\text{\textsubscript{\(\rho\)}}}
% 
% \DeclareMathOperator{\e}{e}
% \DeclareMathOperator{\TE}{TE}
% %\DeclareMathOperator{\indx}{indx}  % A variable in pseudocode
% \newcommand{\indx}{B}
% 
% \hyphenation{Lii-ma-tai-nen}
% 
% %\journal{Artificial Intelligence in Medicine}
% \journal{}
% 
% %%%%%%%%%%%%%%%%%%%%%%%
% %% Elsevier bibliography styles
% %%%%%%%%%%%%%%%%%%%%%%%
% %% To change the style, put a % in front of the second line of the current style and
% %% remove the % from the second line of the style you would like to use.
% %%%%%%%%%%%%%%%%%%%%%%%
% %% Numbered
% \bibliographystyle{model1-num-names}
% %% Numbered without titles
% %\bibliographystyle{model1a-num-names}
% %% Harvard
% %\bibliographystyle{model2-names.bst}\biboptions{authoryear}
% %% Vancouver numbered
% %\usepackage{numcompress}\bibliographystyle{model3-num-names}
% %% Vancouver name/year
% %\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}
% %% APA style
% %\bibliographystyle{model5-names}\biboptions{authoryear}
% %% AMA style
% %\usepackage{numcompress}\bibliographystyle{model6-num-names}
% %% `Elsevier LaTeX' style
% %\bibliographystyle{elsarticle-num}
% %%%%%%%%%%%%%%%%%%%%%%%
% 
% \begin{document}
% 
% \begin{frontmatter}
% 
% 
% 
% \begin{abstract}
% \input{chapters/0-abstract}
% \end{abstract}
% 
% \begin{keyword}
% MRI \sep prostate cancer \sep texture analysis \sep
% Gleason score classification \sep computer-aided diagnostics
% %\MSC[2010] 00-01\sep  99-00
% \end{keyword}
% 
% \end{frontmatter}
% 
% \linenumbers
% 
% \include{chapters/1-introduction}
% \include{chapters/2-methods}
% \include{chapters/3-results}
% \include{chapters/4-discussion}
% \include{chapters/5-acknowledgements}
% \include{chapters/6-tables}
% \include{chapters/7-figures}
% \include{chapters/8-captions}
% 
% \section*{References}
% \bibliography{library}
% 
% \end{document}

>>>>

% Use Unicode characters when possible
%\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

@@

% Use nameref to cite supporting information files (see Supporting Information
% section for more info)
\usepackage{nameref,hyperref}

@@

%\DeclareUnicodeCharacter{03C3}{\(\sigma\)}
\DeclareUnicodeCharacter{2096}{\text{\textsubscript{k}}}
\DeclareUnicodeCharacter{2098}{\text{\textsubscript{m}}}
\DeclareUnicodeCharacter{2081}{\text{\textsubscript{1}}}
\DeclareUnicodeCharacter{2082}{\text{\textsubscript{2}}}
\DeclareUnicodeCharacter{1D68}{\text{\textsubscript{\(\rho\)}}}

\DeclareMathOperator{\e}{e}
\DeclareMathOperator{\TE}{TE}
%\DeclareMathOperator{\indx}{indx}  % A variable in pseudocode
\newcommand{\indx}{B}

% \floatname{algorithm}{Pseudo code}
% \renewcommand{\algorithmicrequire}{\textbf{Input:}}
% \renewcommand{\algorithmicensure}{\textbf{Output:}}
% \renewcommand{\algorithmiccomment}[1]{\hspace{1em}\emph{\{#1\}}}
%
% %\newcommand{\tss}[1]{\textsubscript{#1}}
% %\newcommand{\tSs}[1]{\textsuperscript{#1}}
%
% %%\newcommand{\texttwosuperior}{\(^2\)}  % Unicode character ²
% %\newcommand{\texttwosuperior}{\textsuperscript{2}}  % Unicode character ²
% %\newcommand{\texttimes}{\(\times\)}  % Unicode character ×
% %\newcommand{\textmu}{\(\mu\)}  % Unicode character ×
%
% \renewcommand{\vec}[1]{\mathbf{#1}}  % Vectors and matrices.

@@

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
% Please use "sentence case" for title and headings (capitalize only the first
% word in a title (or heading), the first word in a subtitle (or subheading),
% and any proper nouns).
% % \title{Machine learning of prostate MRI: towards improved non-invasive
% % prostate cancer characterization}
\textbf\newline{Machine learning of prostate MRI:\ towards improved non-invasive
prostate cancer characterization}
}
\newline
% Insert author names, affiliations and corresponding author email (do not
% include titles, positions, or degrees).
\\
%Name Surname\textsuperscript{1,2*\textcurrency},
Jussi~Toivonen\textsuperscript{1,2*},
Ileana~Montoya~Perez\textsuperscript{1,2},
Parisa~Movahedi\textsuperscript{1,2},
Harri~Merisaari\textsuperscript{1,2,3},
Marko~Pesola\textsuperscript{1},
Pekka~Taimen\textsuperscript{4},
Peter~J.~Boström\textsuperscript{5},
Jonne~Pohjankukka\textsuperscript{2},
Aida~Kiviniemi\textsuperscript{1,6},
Tapio~Pahikkala\textsuperscript{2},
Hannu~J.~Aronen\textsuperscript{1,6},
Ivan~Jambor\textsuperscript{1,7}
\\
\bigskip
%\textbf{1} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\textbf{1} \deptdr, \utu, \turku\\
\textbf{2} \deptft, \utu, \turku\\
\textbf{3} Turku PET Centre, \utu, \turku\\
\textbf{4} Dept.\ of Pathology, \utu{} and \tyks, \turku\\
\textbf{5} Dept.\ of Urology, \tyks, \turku\\
\textbf{6} Medical Imaging Centre of Southwest Finland, \tyks, \turku\\
\textbf{7} Dept.\ of Radiology, University of Massachusetts---Baystate,
Springfield, MA, USA\\
\bigskip

@@

\end{flushleft}
% Please keep the abstract below 300 words
\section*{Abstract}
%Lorem ipsum dolor sit amet, consectetur adipiscing elit. Curabitur eget porta erat. Morbi consectetur est vel gravida pretium. Suspendisse ut dui eu ante cursus gravida non sed sem. Nullam sapien tellus, commodo id velit id, eleifend volutpat quam. Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus. Nunc pellentesque pretium diam, quis maximus dolor faucibus id. Nunc convallis sodales ante, ut ullamcorper est egestas vitae. Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.
\input{chapters/0-abstract}

@@

%% \include{chapters/1-introduction}
%% \include{chapters/2-methods}
%% \include{chapters/3-results}
%% \include{chapters/4-discussion}
%% \include{chapters/5-acknowledgements}
%% \include{chapters/6-tables}
%% \include{chapters/7-figures}
%% \include{chapters/8-captions}

@@

% Place tables after the first paragraph in which they are cited.
\begin{table}[!ht]
% Comment out/remove adjustwidth environment if table fits in text column.
\begin{adjustwidth}{-2.25in}{0in}
\centering
\caption{
{\bf Table caption Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam.}}
\begin{tabular}{|l+l|l|l|l|l|l|l|}
\hline
\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \thickhline
$cell1 row1$ & cell2 row 1 & cell3 row 1 & cell4 row 1 & cell5 row 1 & cell6 row 1 & cell7 row 1 & cell8 row 1\\ \hline
$cell1 row2$ & cell2 row 2 & cell3 row 2 & cell4 row 2 & cell5 row 2 & cell6 row 2 & cell7 row 2 & cell8 row 2\\ \hline
$cell1 row3$ & cell2 row 3 & cell3 row 3 & cell4 row 3 & cell5 row 3 & cell6 row 3 & cell7 row 3 & cell8 row 3\\ \hline
\end{tabular}
\begin{flushleft} Table notes Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl. Ut ornare mauris tellus, vel dapibus arcu suscipit sed.
\end{flushleft}
\label{table1}
\end{adjustwidth}
\end{table}

% PLOS does not support heading levels beyond the 3rd (no 4th level headings).
\subsection*{\lorem\ and \ipsum\ nunc blandit a tortor}
\subsubsection*{3rd level heading}
Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque. Quisque augue sem, tincidunt sit amet feugiat eget, ullamcorper sed velit. Sed non aliquet felis. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Mauris commodo justo ac dui pretium imperdiet. Sed suscipit iaculis mi at feugiat.

@@

% Include only the SI item label in the paragraph heading. Use the
% \nameref{label} command to cite SI items in the text.
\paragraph*{S1 Fig.}
\label{S1_Fig}
{\bf Bold the title sentence.} Add descriptive text after the title of the item (optional).

@@

% \usepackage[T1]{fontenc}
% \usepackage[utf8]{inputenc}
% %\usepackage{latexsym}
% \usepackage[abbreviations = true]{siunitx}
% \usepackage{algorithmic, algorithm}
% %\hypersetup{colorlinks,%
% %    citecolor=blue,%
% %    filecolor=blue,%
% %    linkcolor=blue,%
% %    urlcolor=blue,%
% %    unicode
% %    }
%
% \sisetup{detect-all = true,
%   text-rm = \sffamily,
%   per-mode = symbol,
%   literal-superscript-as-power = true
%   }
% %\DeclareSIUnit \umm{\square\um}
% \modulolinenumbers[5]
%
%
%
% \hyphenation{Lii-ma-tai-nen}
%
% %\journal{Artificial Intelligence in Medicine}
% \journal{}
%
% %%%%%%%%%%%%%%%%%%%%%%%
% %% Elsevier bibliography styles
% %%%%%%%%%%%%%%%%%%%%%%%
% %% To change the style, put a % in front of the second line of the current style and
% %% remove the % from the second line of the style you would like to use.
% %%%%%%%%%%%%%%%%%%%%%%%
% %% Numbered
% \bibliographystyle{model1-num-names}
% %% Numbered without titles
% %\bibliographystyle{model1a-num-names}
% %% Harvard
% %\bibliographystyle{model2-names.bst}\biboptions{authoryear}
% %% Vancouver numbered
% %\usepackage{numcompress}\bibliographystyle{model3-num-names}
% %% Vancouver name/year
% %\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}
% %% APA style
% %\bibliographystyle{model5-names}\biboptions{authoryear}
% %% AMA style
% %\usepackage{numcompress}\bibliographystyle{model6-num-names}
% %% `Elsevier LaTeX' style
% %\bibliographystyle{elsarticle-num}
% %%%%%%%%%%%%%%%%%%%%%%%
%
% \begin{document}
%
% \begin{frontmatter}
%
%
%
% \begin{abstract}
% \input{chapters/0-abstract}
% \end{abstract}
%
% \begin{keyword}
% MRI \sep prostate cancer \sep texture analysis \sep
% Gleason score classification \sep computer-aided diagnostics
% %\MSC[2010] 00-01\sep  99-00
% \end{keyword}
%
% \end{frontmatter}
%
% \linenumbers
%
% \section*{References}
% \bibliography{library}
%
% \end{document}
